---
title: "Corolla Pricing Model"
format: html
editor: visual
---

------------------------------------------------------------------------

```{r}
#| message: false
library(tidyverse)
library(rpart)
library(rpart.plot)
library(caret)
library(ggthemes)
library(gamlr)
library(readr)
library(dplyr)
library(ggplot2)
library(iml)
```

## Read in and Prepare Data

```{r}
cars <- read_csv("ToyotaCorolla.csv")
str(data)
sum(is.na(data()))
```

```{r}
cars = cars %>%
  select(-Id, -Model, -Mfg_Month, -Cylinders, -Quarterly_Tax)
```

Important Features

-   Mileage (Kilometers): use, wear-and-tear, how much life left.

-   Age (months/years): age-related wear like rust.

```{r}
cars %>%
    select(Mfg_Year) %>%
    table()

```

```{r}
cars = cars %>% 
  mutate_at(vars(Mfg_Year, 
                 Fuel_Type,
                 Color), .funs = factor)
```

## Analyzing the Price Variable

```{r}
cars %>%
  ggplot(aes(x=Price)) + 
  geom_histogram(aes(y=after_stat(density)),
                 fill = "aquamarine",
                 color = "aquamarine3",
                 alpha = 0.7) +
  geom_density(color = "black") +
  labs(title = "Distribution of Car Prices",
       x = "Price") +
  theme_clean()
```

```{r}
hist(cars$Price)
summary(cars$Price)
```

## Relation between Price & Other Features

```{r}
plot(cars$Age_08_04, cars$Price, main = "Scatterplot of Price vs. Age_08_04", xlab = "Mfg_Year", ylab = "Price")
cor(cars$Price, cars$Age_08_04)
```

```{r}
plot(cars$KM, cars$Price, main = "Scatterplot of Price vs. Mileage", xlab = "Mileage", ylab = "Price")
cor(cars$Price, cars$KM)
```

Earlier I noted that age and mileage are important features to this data set so I graphed the relationship between age vs price & mileage vs price. The scatterplots shows that age nor mileage really have a strong linear impact on car prices.

## Strongly Related Variables

```{r}
library(reshape2)
cars$Mfg_Year <- as.numeric(as.character(cars$Mfg_Year))
numeric_data <- cars[, c("Price", "Mfg_Year", "KM", "HP", "Age_08_04")]
cor_matrix <- cor(numeric_data)
melted_cor <- melt(cor_matrix)

cars %>%
  ggplot(aes(data = melted_cor, x = "Var1", y = "Var2", fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "blue", high = "red") +
  labs(x = "Variable", y = "Variable") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
```

## Partitioning Data

```{r}
set.seed(123)
train_index <- createDataPartition(cars$Price, p = 0.7, list = FALSE)
train_data <- cars[train_index, ]
test_data <- cars[-train_index, ]
```

## Regression Tree Model

```{r}
tree_model <- train(Price ~ ., data = train_data, method = "rpart", trControl = trainControl(method = "cv"))
rpart.plot(tree_model$finalModel)
```

## Removing Unwanted Features & Comparing Data

```{r}
train_data <- train_data[, c("Price", "Age_08_04", "KM", "HP")]
tree_model <- rpart(train_data$Price - train_data$Age_08_04 + train_data$KM + train_data$HP, data = train_data)
```

```{r}
library(caret)
best <- tree_model$bestTune$cp[which.min((tree_model$bestTune$cp)[,"xerror"]), "CP"]
pruned_tree <- prune(tree_model,cp=best) 
predictions <- predict(pruned_tree, newdata = test_data)
rmse <- sqrt(mean((predictions - test_data$Price)^2))
rsme
```

```{r}
colnames(cars)
head(cars)
```
